Metadata control

### 2023-05-04 metadata/metadata_control.Rmd
Removing rownames from taxa metabs
Refining metadata, moving custom stans to own spreadsheet

```{r samp_log from sample log}
if(!file.exists("raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx")){
  stop("Go download the data from email, search 'MESO_SCOPE_Cruise_KM1709_Sample_Log'")
  # Needs to be converted to .xlsx and downloaded
}
if(!file.exists("raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx")){
  stop("Go download the data from email, search 'FALKOR- Sample Log_INGALLS'")
  # Needs to be converted to .xlsx and downloaded
}
bottle_depth_data <- read_csv("made_data/bottle_depth_data.csv")
MT_samps <- "raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx" %>%
  read_excel(sheet = "Metabolites_and_Proteins", range = "A2:J114") %>%
  mutate(cruise="MT") %>%
  select(cruise, station=Station, cast=Cast, depth=`Depth (m)`, 
         rosette=`Niskin #`, id=`Sample ID`) %>%
  filter(complete.cases(.)) %>%
  mutate(station=str_remove(station, "^S")) %>%
  mutate(cast=as.numeric(str_remove(cast, "^C"))) %>%
  # We can grab DCM values here or from the mini DCM spreadsheet I made later
  # mutate(abs_depth=as.numeric(str_remove(depth, "DCM="))) %>%
  mutate(depth=str_replace(depth, ".0", "m")) %>%
  mutate(depth=str_replace(depth, "=.*", "")) %>%
  # Guessing at rosette number here - doesn't really matter bc we're matching
  # based on station more than exact rosette mostly and all bottles
  # were fired at similar depths and times
  mutate(rosette=ifelse(rosette=="?", 1, rosette)) %>% 
  mutate(rosette=as.numeric(rosette)) %>%
  # Fixing likely transcription error - sample looks like 15m samples and
  # all other triplicates were 19, 20, and 21
  mutate(rosette=ifelse(rosette==4 & cast==3 & station=="6", 21, rosette)) %>%
  left_join(bottle_depth_data)
MC_samps <- "raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx" %>%
  read_excel(sheet = "Metabolites_High_Resolution", range = "A2:J35") %>%
  mutate(cruise="MC") %>%
  select(cruise, station=Station, cast=Cast, depth=`Depth (m)`, 
         rosette=`Niskin #`, id=`Sample ID`) %>%
  filter(!is.na(station)) %>%
  mutate(station=str_remove(station, "^S")) %>%
  mutate(cast=as.numeric(str_remove(cast, "^C"))) %>%
  mutate(rosette=as.numeric(rosette)) %>%
  mutate(depth=str_replace(depth, "\\-", "less")) %>%
  mutate(depth=str_replace(depth, "\\+", "plus")) %>%
  mutate(id=str_remove(id, "^MHR")) %>%
  left_join(bottle_depth_data)
samp_log <- bind_rows(MT_samps, MC_samps)
```

```{r file_metadata from mzML list}
samp_metadata <- list.files("../mzMLs/pos", pattern = "Smp.*mzML") %>%
  data.frame(filename=.) %>%
  mutate(samp_type="Smp") %>%
  mutate(cruise=case_when(
    str_detect(filename, "180205") ~ "MC",
    str_detect(filename, "180821") ~ "MT",
    str_detect(filename, "190715") ~ "FK",
    TRUE ~ "Unknown"
  )) %>%
  mutate(station=str_extract(filename, "((?<=S)\\d+)|L\\d")) %>%
  mutate(cast=case_when(
    cruise=="MC" ~ str_extract(filename, "(?<=C)\\d+"),
    cruise=="MT" ~ str_extract(filename, "(?<=C)\\d"),
    cruise=="FK" ~ "1",
  )) %>%
  mutate(cast=as.numeric(cast)) %>%
  mutate(depth=str_extract(filename, "15m|25m|DCM(plus|less)?(10m|20m)?|175m")) %>%
  mutate(tripl=str_extract(filename, "(?<=_)[A-C](?=.mzML$)")) %>%
  mutate(untripl=str_replace(filename, "_[A-C].mzML$", "")) %>%
  mutate(date_run=str_extract(filename, "^\\d+")) %>%
  mutate(date_run=strptime(date_run, format = "%y%m%d")) %>%
  mutate(id=str_extract(filename, "(?<=_)(MS|L).*_[A-C](?=.mzML$)")) %>%
  mutate(id=str_replace(id, "less", "-")) %>%
  mutate(id=str_replace(id, "plus", "+"))
absolute_depths <- samp_metadata %>%
  distinct(station, depth) %>%
  mutate(depth_diff=sapply(depth, function(depth){
    depth_num <- str_extract(depth, "(?<=DCM(plus|less))\\d*")
    depth_num <- ifelse(is.na(depth_num), 0, depth_num)
    depth_sign <- sapply(str_extract(depth, "less|plus"), 
                         switch, "plus"=1, "less"=-1, 0, USE.NAMES = FALSE)
    as.numeric(depth_num)*depth_sign
  })) %>%
  left_join(read.csv("raw_data/all_DCMs.csv")) %>%
  mutate(abs_depth=DCM_depth+depth_diff) %>%
  mutate(abs_depth=ifelse(str_detect(depth, "DCM"), abs_depth, 
                          as.numeric(str_extract(depth, "^\\d+")))) %>%
  select(station, cast, depth, abs_depth)
samp_metadata <- samp_metadata %>%
  left_join(absolute_depths) %>%
  left_join(samp_log, by=c("cruise", "station", "cast", "depth", "id")) %>%
  # If we have an exact depth for a given bottle, use it, otherwise trust
  # the depth extracted from sample sheets or file names
  mutate(abs_depth = ifelse(is.na(pressure), abs_depth, pressure)) %>%
  select(-pressure)

extra_metadata <- list.files("../mzMLs/pos", pattern = "Blk|Std|Poo.*mzML") %>%
  data.frame(filename=.) %>%
  mutate(samp_type=str_extract(filename, "Std|Blk|Poo")) %>%
  mutate(cruise=case_when(
    str_detect(filename, "170706") ~ "MC",
    str_detect(filename, "180205") ~ "MC",
    str_detect(filename, "180821") ~ "MT",
    str_detect(filename, "190715") ~ "FK",
    TRUE ~ "Unknown"
  )) %>%
  mutate(date_run=str_extract(filename, "^\\d+")) %>%
  mutate(date_run=strptime(date_run, format = "%y%m%d"))

if(!file.exists("made_data/file_timestamps.csv")){
  list.files("../mzMLs/pos", pattern = "mzML", full.names = TRUE) %>%
    grabMSdata(grab_what = "metadata") %>%
    `$`("metadata") %>%
    select(filename, timestamp) %>%
    write.csv("made_data/file_timestamps.csv", row.names = FALSE)
}
file_timestamps <- read_csv("made_data/file_timestamps.csv") %>%
  fill(timestamp, .direction = "up")

file_metadata <- bind_rows(samp_metadata, extra_metadata) %>%
  left_join(file_timestamps) %>%
  arrange(timestamp) %>%
  # Just reordering, nothing getting dropped
  select(c("filename", "samp_type", "cruise", "station", "cast", "depth", 
           "abs_depth", "rosette", "tripl", "id", "untripl", "date_run", 
           "timestamp"))
write.csv(file_metadata, file = "made_data/file_metadata.csv", row.names = FALSE)
```

@@

```{r heatmaply metadata}
filled_MT_metadata <- filled_file_metadata %>%
  filter(cruise=="FK") %>%
  filter(samp_type=="Smp") %>%
  select(where(~!all(is.na(.x))))

@@

```{r ggally pairsplot}
filled_MT_metadata <- filled_file_metadata %>%
  filter(cruise=="MT") %>%
  mutate(depth=factor(depth, levels = c("15m", "DCM", "175m")))

library(GGally)
filled_MT_metadata %>%
  select(station, depth, abs_depth, time, lat, sla, local_hour, alk, dic, ph, 
         ends_with("um"), ends_with("ug"), ends_with("abund")) %>%
  ggpairs(aes(color=depth)) %>%
  ggsave(filename = "MT_ggpairsplot.pdf", device = "pdf", path = "figures", 
         width = 30, height = 30, units = "in", dpi = 300)
```

## PCA groupings

```{r pca, eval=FALSE}
filled_MT_metadata <- read_csv("made_data/filled_file_metadata.csv") %>%
  filter(cruise=="MT") %>%
  filter(samp_type=="Smp") %>%
  mutate(depth=factor(depth, levels = c("15m", "DCM", "175m")))

pca_output <- filled_MT_metadata %>%
  select(filename, abs_depth, time, lat, sla, local_hour, #alk, dic, ph, 
         ends_with("abund"), ends_with("um"), ends_with("ug"),
         beam_atten, -oxy_um) %>%
  column_to_rownames("filename") %>%
  data.matrix() %>%
  scale() %>%
  prcomp()
# plot(pca_output)
biplot(pca_output)
biplot(pca_output, choices = c(3, 4))

ggpca_data <- pca_output$x %>%
  as.data.frame() %>%
  rownames_to_column("filename") %>%
  select(filename, PC1:PC4) %>%
  left_join(filled_MT_metadata)
ggpca_arrows <- pca_output$rotation %>% 
  `*`(10) %>%
  as.data.frame() %>%
  rownames_to_column("env_param")
ggpca_labels <- ggpca_arrows %>% 
  mutate(PC2=PC2+0.2) %>%
  mutate(PC2=case_when(
    env_param=="sla"~PC2-0.4,
    env_param=="PC_um"~PC2+0.2,
    env_param=="phaeo_ug"~PC2+0.2,
    TRUE~PC2)) %>%
  mutate(PC4=PC4+0.3)
ggplot(mapping = aes(x=PC1, y=PC2)) + 
  geom_point(data = ggpca_data, aes(color=depth)) +
  geom_segment(data = ggpca_arrows, aes(xend=0, yend=0), 
               arrow = arrow(length = unit(0.02, "npc"), ends = "first")) +
  geom_label(data = ggpca_labels, aes(label=env_param)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.8))
ggsave(filename = "MT_PC1_PC2.png", device = "png", path = "figures", 
       width = 5, height = 5, dpi = 144, units = "in", type="cairo")
ggplot(mapping=aes(x=PC3, y=PC4)) + 
  geom_point(data=ggpca_data, aes(color=sla, size=lat)) +
  geom_segment(data = ggpca_arrows, aes(xend=0, yend=0), 
               arrow = arrow(length = unit(0.02, "npc"), ends = "first")) +
  geom_label(data = ggpca_labels, aes(label=env_param)) +
  theme_bw()
ggsave(filename = "MT_PC3_PC4.png", device = "png", path = "figures", 
       width = 5.5, height = 5, dpi = 144, units = "in", type="cairo")
```

@@

```{r grabstans}
if(!file.exists("raw_data/raw_stans.csv")){
  raw_stans <- read.csv(paste0(
    "https://raw.githubusercontent.com/IngallsLabUW/Ingalls_Standards",
    "/master/Ingalls_Lab_Standards.csv"
  ))
  write.csv(raw_stans, file = "raw_data/raw_stans.csv", row.names = FALSE)
}
raw_stans <- read.csv("raw_data/raw_stans.csv")
clean_stans <- raw_stans %>%
  filter(Column=="HILIC") %>%
  mutate(polarity=ifelse(str_detect(z, "-"), "neg", "pos")) %>%
  mutate(mz=as.numeric(mz)) %>%
  mutate(peak_quality=str_extract(Peak_Quality, "Yes|No|Problematic")) %>%
  select(compound_type=Compound_Type, compound_name=Compound_Name,
         compound_name_old=Compound_Name_Original,
         formula=Empirical_Formula, rt=RT_minute, mz=mz, 
         ionization_form=Ionization_Form,
         charge=z, kegg_id=KEGG_Code, polarity, conc_um=Concentration_uM,
         date_added=Date_Added, mix=HILIC_Mix, priority=Priority,
         peak_quality) %>%
  add_row(compound_type="Custom", compound_name="Bisulfate",
          compound_name_old="Bisulfate", formula="HSO4", rt=13, 
          mz=95.95172965+1.007276, ionization_form="[M]", 
          charge=-1, date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine81",
          compound_name_old="Bromine upper", formula="Br(81)", rt=7, 
          mz=80.91563, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Bromine79",
          compound_name_old="Bromine lower", formula="Br(79)", rt=7, 
          mz=78.91768, ionization_form="[M]", charge=-1, 
          date_added=150101, polarity="neg") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamine?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=11, 
          mz=130.050419, ionization_form="[M-NH3+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Pyro from glutamate?",
          compound_name_old=compound_name, formula="C5H7NO3", rt=12, 
          mz=130.050419, ionization_form="[M-H2O+H]", charge=-1, 
          date_added=150101, polarity="pos") %>%
  # add_row(compound_type="Custom", compound_name="Deoxyguanosine?",
  #         compound_name_old=compound_name, formula="C10H13N5O4", rt = 4.5,
  #         mz=268.10403, ionization_form="[M+H]", charge=1, 
  #         date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Deoxycytidine?",
          compound_name_old=compound_name, formula="C10H13N5O4", rt = 6.6,
          mz=228.09788, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Homoserine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 6.7,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Threonine betaine?",
          compound_name_old=compound_name, formula="C7H15NO3", rt = 5,
          mz=162.1125, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Theanine?",
          compound_name_old=compound_name, formula="C7H14N2O3", rt = 6.8,
          mz=175.10771, ionization_form="[M+H]", charge=1, 
          date_added=150101, polarity="pos") %>%
  add_row(compound_type="Custom", compound_name="Asterina-330",
          compound_name_old=compound_name, formula="C12H20N2O6", rt = 10.5,
          mz=289.1393, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Shinorine",
        compound_name_old=compound_name, formula="C13H20N2O8", rt = 11.6,
        mz=333.1292, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Palythine",
        compound_name_old=compound_name, formula="C10H16N2O5", rt = 11.0,
        mz=245.1132, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Porphyra-334?",
        compound_name_old=compound_name, formula="C14H22N2O8", rt = 8.1,
        mz=347.1449, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Mycosporine-2-glycine?",
        compound_name_old=compound_name, formula="C12H18N2O7", rt = 11.3,
        mz=303.1186, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Palythene/Usujirene?",
        compound_name_old=compound_name, formula="C13H20N2O5", rt = 8.3,
        mz=285.1445, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Also Palythene/Usujirene?",
        compound_name_old=compound_name, formula="C13H20N2O5", rt = 6.9,
        mz=285.1445, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Mycosporine-glycine?",
        compound_name_old=compound_name, formula="C10H15NO6", rt = 10,
        mz=246.0972, ionization_form="[M+H]", charge=1) %>%
  add_row(compound_type="Custom", compound_name="Also mycosporine-glycine?",
        compound_name_old=compound_name, formula="C10H15NO6", rt = 9.5,
        mz=246.0972, ionization_form="[M+H]", charge=1) %>%
  mutate(date_added=strptime(x = date_added, format = "%y%m%d"))
write.csv(clean_stans, file = "made_data/clean_stans.csv", row.names = FALSE)
```

## Culture data ----

@@

write.csv(taxa_metabs, file = "made_data/taxa_metabs.csv")
```

>>>>

```{r samp_log from sample log}
if(!file.exists("raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx")){
  stop("Go download the data from email, search 'MESO_SCOPE_Cruise_KM1709_Sample_Log'")
  # Needs to be converted to .xlsx and downloaded
}
bottle_depth_data <- read_csv("made_data/bottle_depth_data.csv")
MT_samps <- "raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx" %>%
  read_excel(sheet = "Metabolites_and_Proteins", range = "A2:J114") %>%
  mutate(cruise="MT") %>%
  select(cruise, station=Station, cast=Cast, depth=`Depth (m)`, 
         rosette=`Niskin #`, id=`Sample ID`) %>%
  filter(complete.cases(.)) %>%
  mutate(station=str_remove(station, "^S")) %>%
  mutate(cast=as.numeric(str_remove(cast, "^C"))) %>%
  # We can grab DCM values here or from the mini DCM spreadsheet I made later
  # mutate(abs_depth=as.numeric(str_remove(depth, "DCM="))) %>%
  mutate(depth=str_replace(depth, ".0", "m")) %>%
  mutate(depth=str_replace(depth, "=.*", "")) %>%
  # Guessing at rosette number here - doesn't really matter bc we're matching
  # based on station more than exact rosette mostly and all bottles
  # were fired at similar depths and times
  mutate(rosette=ifelse(rosette=="?", 1, rosette)) %>% 
  mutate(rosette=as.numeric(rosette)) %>%
  # Fixing likely transcription error - sample looks like 15m samples and
  # all other triplicates were 19, 20, and 21
  mutate(rosette=ifelse(rosette==4 & cast==3 & station=="6", 21, rosette)) %>%
  left_join(bottle_depth_data)
MC_samps <- "raw_data/MESO_SCOPE_Cruise_KM1709_Sample_Log.xlsx" %>%
  read_excel(sheet = "Metabolites_High_Resolution", range = "A2:J35") %>%
  mutate(cruise="MC") %>%
  select(cruise, station=Station, cast=Cast, depth=`Depth (m)`, 
         rosette=`Niskin #`, id=`Sample ID`) %>%
  filter(!is.na(station)) %>%
  mutate(station=str_remove(station, "^S")) %>%
  mutate(cast=as.numeric(str_remove(cast, "^C"))) %>%
  mutate(rosette=as.numeric(rosette)) %>%
  mutate(depth=str_replace(depth, "\\-", "less")) %>%
  mutate(depth=str_replace(depth, "\\+", "plus")) %>%
  mutate(id=str_remove(id, "^MHR")) %>%
  left_join(bottle_depth_data)
samp_log <- bind_rows(MT_samps, MC_samps)
```

```{r file_metadata from mzML list}
samp_metadata <- list.files("../mzMLs", pattern = "Smp.*mzML", recursive = TRUE) %>%
  data.frame(filename=.) %>%
  mutate(polarity=dirname(filename)) %>%
  mutate(filename=basename(filename)) %>%
  mutate(samp_type="Smp") %>%
  mutate(cruise=case_when(
    str_detect(filename, "180205") ~ "MC",
    str_detect(filename, "180821") ~ "MT",
    str_detect(filename, "190715") ~ "FK",
    TRUE ~ "Unknown"
  )) %>%
  mutate(station=str_extract(filename, "((?<=S)\\d+)|L\\d")) %>%
  mutate(cast=case_when(
    cruise=="MC" ~ str_extract(filename, "(?<=C)\\d+"),
    cruise=="MT" ~ str_extract(filename, "(?<=C)\\d"),
    cruise=="FK" ~ "1",
  )) %>%
  mutate(cast=as.numeric(cast)) %>%
  mutate(depth=str_extract(filename, "15m|25m|DCM(plus|less)?(10m|20m)?|175m")) %>%
  mutate(tripl=str_extract(filename, "(?<=_)[A-C](?=.mzML$)")) %>%
  mutate(untripl=str_replace(filename, "_[A-C].mzML$", "")) %>%
  mutate(date_run=str_extract(filename, "^\\d+")) %>%
  mutate(date_run=strptime(date_run, format = "%y%m%d")) %>%
  mutate(id=str_extract(filename, "(?<=_)(MS|L).*_[A-C](?=.mzML$)")) %>%
  mutate(id=str_replace(id, "less", "-")) %>%
  mutate(id=str_replace(id, "plus", "+"))
absolute_depths <- samp_metadata %>%
  distinct(station, depth) %>%
  mutate(depth_diff=sapply(depth, function(depth){
    depth_num <- str_extract(depth, "(?<=DCM(plus|less))\\d*")
    depth_num <- ifelse(is.na(depth_num), 0, depth_num)
    depth_sign <- sapply(str_extract(depth, "less|plus"), 
                         switch, "plus"=1, "less"=-1, 0, USE.NAMES = FALSE)
    as.numeric(depth_num)*depth_sign
  })) %>%
  left_join(read.csv("raw_data/all_DCMs.csv")) %>%
  mutate(abs_depth=DCM_depth+depth_diff) %>%
  mutate(abs_depth=ifelse(str_detect(depth, "DCM"), abs_depth, 
                          as.numeric(str_extract(depth, "^\\d+")))) %>%
  select(station, cast, depth, abs_depth)
samp_metadata <- samp_metadata %>%
  left_join(absolute_depths) %>%
  left_join(samp_log, by=c("cruise", "station", "cast", "depth", "id")) %>%
  # If we have an exact depth for a given bottle, use it, otherwise trust
  # the depth extracted from sample sheets or file names
  mutate(abs_depth = ifelse(is.na(pressure), abs_depth, pressure)) %>%
  select(-pressure)

extra_metadata <- list.files("../mzMLs", pattern = "Blk|Std|Poo.*mzML", recursive = TRUE) %>%
  data.frame(filename=.) %>%
  mutate(polarity=dirname(filename)) %>%
  mutate(filename=basename(filename)) %>%
  mutate(samp_type=str_extract(filename, "Std|Blk|Poo")) %>%
  mutate(cruise=case_when(
    str_detect(filename, "170706") ~ "MC",
    str_detect(filename, "180205") ~ "MC",
    str_detect(filename, "180821") ~ "MT",
    str_detect(filename, "190715") ~ "FK",
    TRUE ~ "Unknown"
  )) %>%
  mutate(date_run=str_extract(filename, "^\\d+")) %>%
  mutate(date_run=strptime(date_run, format = "%y%m%d"))

if(!file.exists("made_data/file_timestamps.csv")){
  bind_rows(samp_metadata, extra_metadata) %>%
    mutate(filepath=paste("../mzMLs/", polarity, filename, sep = "/")) %>%
    pull(filepath) %>%
    grabMSdata(grab_what = "metadata") %>%
    `$`("metadata") %>%
    select(filename, timestamp) %>%
    write.csv("made_data/file_timestamps.csv", row.names = FALSE)
}
file_timestamps <- read_csv("made_data/file_timestamps.csv") %>%
  fill(timestamp, .direction = "up")

file_metadata <- bind_rows(samp_metadata, extra_metadata) %>%
  left_join(file_timestamps) %>%
  arrange(timestamp) %>%
  # Just reordering, nothing getting dropped
  select(c("filename", "polarity", "samp_type", "cruise", "station", "cast",
           "depth", "abs_depth", "rosette", "tripl", "id", "untripl",
           "date_run", "timestamp"))
write.csv(file_metadata, file = "made_data/file_metadata.csv", row.names = FALSE)
```

@@

```{r heatmaply metadata, purl=FALSE}
filled_MT_metadata <- filled_file_metadata %>%
  filter(cruise=="FK") %>%
  filter(samp_type=="Smp") %>%
  select(where(~!all(is.na(.x))))

@@

@@

```{r grabstans}
if(!file.exists("raw_data/raw_stans.csv")){
  raw_stans <- read.csv(paste0(
    "https://raw.githubusercontent.com/IngallsLabUW/Ingalls_Standards",
    "/master/Ingalls_Lab_Standards.csv"
  ))
  write.csv(raw_stans, file = "raw_data/raw_stans.csv", row.names = FALSE)
}
if(!file.exists("raw_data/custom_stans.csv")){
  custom_stans <- read.csv(paste0(
    "https://raw.githubusercontent.com/IngallsLabUW/Ingalls_Standards",
    "/master/data_extra/custom_stans.csv"
  ))
  write.csv(custom_stans, file = "raw_data/custom_stans.csv", row.names = FALSE)
}
raw_stans <- read.csv("raw_data/raw_stans.csv")
custom_stans <- read.csv("raw_data/custom_stans.csv")
clean_stans <- raw_stans %>%
  bind_rows(custom_stans) %>%
  filter(Column=="HILIC"|Compound_Type=="Custom") %>%
  mutate(polarity=ifelse(str_detect(z, "-"), "neg", "pos")) %>%
  mutate(mz=as.numeric(mz)) %>%
  mutate(peak_quality=str_extract(Peak_Quality, "Yes|No|Problematic")) %>%
  select(compound_type=Compound_Type, compound_name=Compound_Name,
         compound_name_old=Compound_Name_Original,
         formula=Empirical_Formula, rt=RT_minute, mz=mz, 
         ionization_form=Ionization_Form,
         charge=z, kegg_id=KEGG_Code, polarity, conc_um=Concentration_uM,
         date_added=Date_Added, mix=HILIC_Mix, priority=Priority,
         peak_quality) %>%
  mutate(date_added=strptime(x = date_added, format = "%y%m%d"))
write.csv(clean_stans, file = "made_data/clean_stans.csv", row.names = FALSE)
```

## Culture data

@@

write.csv(taxa_metabs, file = "made_data/taxa_metabs.csv", row.names = FALSE)
```
